Library Learning in Neurally-Guided Bayesian Program Learning

### 2018-09-26 nips_2018.tex
acknowledgments and extra citation

The FlashFill system~\cite{gulwani2011automating} developed by
Microsoft researchers and now embedded in Excel solves problems such
as these and is probably the best known practical program-induction
algorithm, but researchers in programming languages and AI have built
successful program induction algorithms for many applications, 
such as handwriting recognition and generation~\cite{lake2015human},
procedural graphics~\cite{ellis2017learning}, question
answering~\cite{johnson2017clevr} and robot motion
planning~\cite{devlin2017neural}, to name just a few.
These systems work in different ways, but most hinge upon having a
carefully engineered \textbf{Domain Specific Language (DSL)}.  This is
especially true for systems such as FlashFill that aim to induce a
wide range of programs very quickly, in a few seconds or less.  DSLs
constrain the search over programs with strong prior knowledge in the
form of a restricted set of programming primitives tuned to the needs
of the domain: for text editing, these are operations like appending
strings and splitting on characters.

@@

 \noindent \textbf{Inventing new subroutines for program induction:}
 Several program induction algorithms, most prominently the EC algorithm~\cite{Dechter:2013:BLV:2540128.2540316}, take as their goal to learn new, reusable subroutines that are shared in a multitask setting. We find this work inspiring and motivating,
 and extend it along two dimensions: (1) we propose a new algorithm for
 inducing reusable subroutines, based on Fragment Grammars~\cite{tim};
 and (2) we show how to combine these techniques with bottom-up neural recognition models.
 Other instances of this related idea are~\cite{DBLP:conf/icml/LiangJK10}, Schmidhuber's OOPS model~\cite{schmidhuber2004optimal}, and predicate invention in Inductive Logic Programming~\cite{DBLP:conf/ecai/LinDETM14}.

\noindent\textbf{Bayesian Program
 Learning:} Our work is an instance of
 Bayesian Program
 Learning (BPL; see~\citep{lake2015human,Dechter:2013:BLV:2540128.2540316,ellis2016sampling,DBLP:conf/icml/LiangJK10}). Previous BPL systems have largely assumed a fixed DSL (but see~\cite{DBLP:conf/icml/LiangJK10}),
 and our contribution here is a general way of doing BPL with less hand-engineering of the DSL.

@@

>>>>

The FlashFill system~\cite{gulwani2011automating} developed by
Microsoft researchers and now embedded in Excel solves problems such
as these and is probably the best known practical program-induction
algorithm, but researchers in programming languages and AI have built
successful program induction algorithms for many applications, such as
handwriting recognition and generation~\cite{lake2015human},
procedural graphics~\cite{ellis2017learning}, cognitive
modeling~\cite{DBLP:journals/cogsr/SchmidK11}, question
answering~\cite{johnson2017clevr} and robot motion
planning~\cite{devlin2017neural}, to name just a few.  These systems
work in different ways, but most hinge upon having a carefully
engineered \textbf{Domain Specific Language (DSL)}.  This is
especially true for systems such as FlashFill that aim to induce a
wide range of programs very quickly, in a few seconds or less.  DSLs
constrain the search over programs with strong prior knowledge in the
form of a restricted set of programming primitives tuned to the needs
of the domain: for text editing, these are operations like appending
strings and splitting on characters.

@@

 \noindent \textbf{Inventing new subroutines for program induction:}
 Several program induction algorithms, most prominently the EC algorithm~\cite{Dechter:2013:BLV:2540128.2540316}, take as their goal to learn new, reusable subroutines that are shared in a multitask setting. We find this work inspiring and motivating,
 and extend it along two dimensions: (1) we propose a new algorithm for
 inducing reusable subroutines, based on Fragment Grammars~\cite{tim};
 and (2) we show how to combine these techniques with bottom-up neural recognition models.
 Other instances of this related idea are~\cite{DBLP:conf/icml/LiangJK10}, Schmidhuber's OOPS model~\cite{schmidhuber2004optimal}, MagicHaskeller~\cite{katayama2015towards}, and predicate invention in Inductive Logic Programming~\cite{DBLP:conf/ecai/LinDETM14}.

\noindent\textbf{Bayesian Program
 Learning:} Our work is an instance of
 Bayesian Program
 Learning (BPL; see~\citep{lake2015human,Dechter:2013:BLV:2540128.2540316,ellis2016sampling,DBLP:conf/icml/LiangJK10,ellis2015unsupervised}). Previous BPL systems have largely assumed a fixed DSL (but see~\cite{DBLP:conf/icml/LiangJK10}),
 and our contribution here is a general way of doing BPL with less hand-engineering of the DSL.

@@

\subsubsection*{Acknowledgments} We are grateful for collaborations with Eyal Dechter, whose EC algorithm directly inspired this work. Funding from NSF GRFP and the MUSE program (Darpa grant FA8750-14-2-0242).
